R Notebook

### 2018-01-09 paper/R/02_cleanAndCombine.Rmd
step

load("../output/news_cleaned.Rda")
okt <- read_csv("../data/eventbride/eventbride_okt_18.csv")
nov_03 <- read_csv("../data/eventbride/eventbride_nov_03.csv")
nov_22 <- read_csv("../data/eventbride/eventbride_nov_22.csv")
nov_30 <- read_csv("../data/eventbride/eventbride_nov_30.csv")
```

@@

```{r}
btw1 <- bind_rows(list(okt,nov_03,nov_22,nov_30)) %>%
  mutate(text = body,
         # Extract site 
         site = str_extract(source, "(?<='uri': ')[A-z][^']*")) %>%
  # Delete duplicates
  #filter(isDuplicate=="False") %>%
  distinct(text, site, .keep_all = TRUE) %>%
  select(date,title,text,site,url)

btw1 <- bind_rows(df %>%
                   mutate(date = as.Date(date)) %>%
                   select(date,title,text,site,url),
                 btw1)
```

# Pre-Process Text
## select news-outlets
```{r}
keeps <- c("welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de","tagesschau.de")

btw1 %>%
  mutate(title_text = paste(title, text, sep=" ")) %>%
  filter(site %in% keeps) -> btw
```

## select politic section
```{r}
pat1 <- "\\w\\.de/politik/deutschland"
pat2 <- "\\w\\.de/politik/inland"
pat3 <- "\\w\\.de/politik/wahl"
pat4 <- "\\w\\.de/politik/bundestagswahl"
pat5 <- "tagesschau\\.de/inland"

btw %>%
  mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,pat5,
                     sep="|"), url, perl = TRUE),1,0)) -> df_full
```

```{r}
df_full %>%
  filter(politics == 1) %>%
  distinct(url, .keep_all = T) -> btw
```

## count number of terms in a string
```{r}
btw$text_length <- sapply(gregexpr("\\S+", btw$text), length)
```

## ... and filter short text & other
```{r}
btw %>%
  filter(text_length > 200) %>%
  # remove articles that contain daily overviews
  filter(!grepl("News des Tages", title_text)) %>%
  filter(!grepl("Nachrichten am Morgen", title)) %>%
  filter(!startsWith(title,"News")) %>%
  # remove articles that only contain video 
  filter(!grepl("Video einbetten Nutzungsbedingungen Embedding Tagesschau", title_text)) %>%
  # remove english text
  filter(!grepl("bild-international", url)) %>%
  filter(!grepl("german",url)) %>%
  # remove text that mostly contain user comments
  filter(!grepl("kommentar", title, ignore.case = TRUE)) %>%
  filter(!grepl("ticker", title, ignore.case = TRUE)) %>%
  filter(!grepl("stream", title, ignore.case = TRUE)) %>%
  filter(!startsWith(text,"1.")) -> btw
```

```{r}
btw %>%
  filter(grepl("faktenfinder", title_text)) %>%
  select(url, title_text)
```

@@

The following two chuncks of code are just to check right regex definitions to use it inthe clean.text function.
```{r}
pat <- "Eine Kolumne von \\w{1,} \\w{1,}"
btw %>%
  filter(grepl(pat, title_text, perl = TRUE, ignore.case = TRUE)) %>%
  #filter(site=="tagesschau.de") %>%
  #select(url, title_text) %>% 
  #.[1,] %>%
  #htmlTable::htmlTable()
  group_by(site) %>%
  tally(sort = TRUE)
```

```{r}
as.data.frame(str_match(btw$title_text, pat)) ->test
test %>%
  filter(!is.na(test)) %>%
  .[1:30,]
```

@@

@@

# apply function to dataframe
btw$text_cleaned <- clean.text(btw$title_text)
```

```{r}
btw$text_cleaned <- gsub("[[:punct:]]", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("[[:cntrl:]]", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("[[:digit:]]", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("^[[:space:]]+", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("[[:space:]]+$", " ", btw$text_cleaned)
btw$text_cleaned <- tolower(btw$text_cleaned)
```

## Remove Stopwords
```{r}
btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
```

### Remove customized stopwords
```{r}
mystopwords <- c("focus","online","spiegel", "stern", "de", "bild","bildplus", "zeit", "ersten", "tagesschau", "zeitmagazin","seitenanfang","ja","mal","heute","ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment","ticker","live","laif","uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv","nwmi","wäre","viele","nwnoa","morgenkolumne","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon","registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen","tba","datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht")

mystopwords <- distinct(as.data.frame(mystopwords))

btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords$mystopwords)
```

### check words with high tf-idf 
```{r}
token <- btw %>%
  group_by(site) %>%
  unnest_tokens(word, title) %>%
  count(site, word, sort = TRUE)  %>%
  bind_tf_idf(word, site, n) %>%
  arrange(desc(tf_idf))

@@

## month & document number
```{r}
btw %>%
  mutate(month = month(date),
         articleID = as.numeric(rownames(btw)),
         site = ifelse(site=="bild.de","Bild.de",site),
         site = ifelse(site=="focus.de","FOCUS ONLINE",site),
         site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
         site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
         site = ifelse(site=="welt.de","DIE WELT",site)) -> btw
```

>>>>

#load("../output/news_cleaned.Rda")
okt <- read_csv("../data/eventbride/eventbride_okt_18.csv")
nov_03 <- read_csv("../data/eventbride/eventbride_nov_03.csv")
nov_22 <- read_csv("../data/eventbride/eventbride_nov_22.csv")
dec_16 <- read_csv("../data/eventbride/eventbride_dec_16.csv")
jan_1 <- read_csv("../data/eventbride/eventbride_jan_1.csv")
```

@@

```{r}
df_full <- bind_rows(list(okt,nov_03,nov_22,dec_16,jan_1)) %>%
  mutate(text = body,
         # Extract site 
         site = str_extract(source, "(?<='uri': ')[A-z][^']*")) %>%
  # Delete duplicates
  #filter(isDuplicate=="False") %>%
  distinct(text, site, .keep_all = TRUE) %>%
  select(date,title,text,site,url)

# df_full <- bind_rows(df %>%
#                    mutate(date = as.Date(date)) %>%
#                    select(date,title,text,site,url),
#                  df_full)
```

# Pre-Process Text
## select news-outlets
```{r}
keeps <- c("spiegel.de", "focus.de", "zeit.de","bild.de",
           "tagesschau.de","deutschlandfunk.de")

df <- df_full %>%
  mutate(title_text = paste(title, text, sep=" ")) %>%
  filter(site %in% keeps) %>%
  filter(date>=as.Date("2017-09-14"))
```

## select politic section
```{r}
# pat1 <- "\\w\\.de/politik/deutschland"
# pat2 <- "\\w\\.de/politik/inland"
# pat3 <- "\\w\\.de/politik/wahl"
# pat4 <- "\\w\\.de/politik/bundestagswahl"
# pat5 <- paste("cdu","csu","union","spd","fdp","afd","linkspartei","gruenen",
#               "merkel","schulz","nahles","gabriel","oezdemir","petry","wagenknecht","lindner",
#               "gauland","weidel","steinmeier","seehofer","maiziere","dreyer","althusmann",
#               "buergermeister", "fraktion","jamaika","groko","koalition","sondierung","btw","wahl",
#               "bundestag","bundewehr","bundesregierung","landtag","minister","kanzler",
#               "fluechtling","raf","glyphosat","rundfunk",  sep="|")
# 
# btw %>%
#   mutate(politics = ifelse(grepl(paste(pat1,pat2,pat3,pat4,
#                       sep="|"), url, perl = TRUE),1,0)) -> btw1
# 
#  
# btw1$politics <- ifelse(btw1$site=="deutschlandfunk.de"&grepl(pat5,btw1$url),1,btw1$politics)
# btw1$politics <- ifelse(btw1$site=="tagesschau.de"&grepl(pat5,btw1$url),1,btw1$politics)

#........................
pat <- paste("cdu","csu","union","spd","fdp","afd",
             "linkspartei","die linke","die grünen","bündnis 90", sep="|")

df %>%
  mutate(politics = ifelse(grepl(pat, title_text, ignore.case = TRUE),1,0)) -> btw1
```

```{r}
btw1 %>%
  #filter(politics==1) %>%
  ggplot(aes(site, fill=factor(politics))) +
  geom_bar(show.legend = FALSE, alpha=0.8)
```

```{r}
btw <- btw1 %>% filter(politics==1)
```

```{r}
btw %>%
  group_by(date, site) %>%
  summarize(obs = n()) %>%
  ggplot(aes(date, obs, fill = factor(site))) +
  geom_col(alpha=0.8) +
  #geom_vline(aes(xintercept=as.Date("2017-09-24")),
  #           linetype = 2, color="grey40") +
  #geom_vline(aes(xintercept=as.Date("2017-11-20")),
  #               linetype = 2, color="grey40") +
  #scale_color_manual(values = col) +
  labs(x="", y="Count",fill="") +
  scale_x_date(breaks = date_breaks("1 week"), labels=date_format("%d.%m", tz="CET"))
```

## count number of terms in a string
```{r}
df$text_length <- sapply(gregexpr("\\S+", df$text), length)
```

## ... and filter short text & other
```{r}
btw <- df %>%
  filter(text_length > 120) %>%
  arrange(desc(text_length)) %>%
  distinct(url, .keep_all = TRUE) %>%

  # remove articles that contain daily overviews
  filter(!grepl("Nachrichten am Morgen", title)) %>%
  filter(!grepl("elbvertiefung", url)) %>%
  filter(!grepl("zeit-magazin", url)) %>%
  filter(!grepl("s-magazin", url)) %>%
  filter(!startsWith(title,"News")) %>%

  # remove articles that only contain video 
  filter(!grepl("Video einbetten Nutzungsbedingungen Embedding Tagesschau", title_text)) %>%

  # remove english text
  filter(!grepl("bild-international", url)) %>%
  filter(!grepl("spiegel.de/international", url)) %>%
  filter(!grepl("german",url)) %>%
  filter(!grepl("arabisch",url)) %>%

  # remove text that mostly contain user comments
  filter(!grepl("ticker", title, ignore.case = TRUE)) %>%
  filter(!grepl("stream", title, ignore.case = TRUE)) %>%
  filter(!startsWith(text,"1.")) 
```

```{r}
save(btw, file="../output/btw_combined.Rda")

rm(list=ls())
load("../output/btw_combined.Rda")
```

@@

The following two chuncks of code are just to check right regex definitions to use it inthe clean.text function.
```{r}
pat <- "Newsletter[^\n]*"
btw %>%
  filter(grepl(pat, title_text, perl = TRUE, ignore.case = TRUE)) %>%
  #filter(site=="tagesschau.de") %>%
  #select(url, title_text) %>% 
  #.[1,] %>%
  #htmlTable::htmlTable()
  group_by(site) %>%
  tally(sort = TRUE)
```

```{r}
btw_test <- btw

as.data.frame(str_match(btw_test$title_text , pat)) ->test

test %>%
  filter(!is.na(test)) %>%
  .[1:30,]
```

@@

  # Deutschlandfunk
  x = gsub("Äußerungen unserer Gesprächspartner[^.]*", "", x, perl = TRUE)
  x = gsub("im Gespräch mit \\w{1,}", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Heinlein", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Barenberg", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Büüsker", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Dobovisek", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Schmidt-Mattern", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Zagatta", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Armbrüster", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Münchenberg", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Heckmann", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Kaess", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Engels", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Zurheide", "", x, ignore.case = TRUE, perl=TRUE)
  x = gsub("Marc Müller", "", x, ignore.case = TRUE, perl=TRUE)

@@

# apply function to dataframe
btw$text_cleaned <- clean.text(btw$title_text)

btw$text_cleaned <- gsub("[[:punct:]]", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("[[:cntrl:]]", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("[[:digit:]]", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("^[[:space:]]+", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("[[:space:]]+$", " ", btw$text_cleaned)
btw$text_cleaned <- tolower(btw$text_cleaned)

## Remove stopwords
# 1
german_stopwords_full <- read.table("dict/german_stopwords_full.txt", stringsAsFactors = F)
german_stopwords_full <- german_stopwords_full$V1

# 2
mystopwords <- c("focus","online","spiegel", "stern", "de", "bild","bildplus","n-tv.de", "zeit", "ersten", "tagesschau","müssen","sagen", "zeitmagazin","seitenanfang","ja","mal","heute","ich","sie","passwort","kommentar","wurde","ihr","der","im","artikel","mehr","ihren","foto","e","seien","comment","ticker","live","laif","uhr","videolänge","dass","mindestens","das","mail","die","schon","neuer abschnitt", "login", "loggen", "inaktiv","nwmi","wäre","viele","nwnoa","morgenkolumne","beim","dpa","video","quelle","afp","witters","fotogalerie","wurden","worden","wegen","sagt","immer","gibt","geht","spon","registrierter","als","spiegel","vielen","in","es","bitte","dank","unserer","nutzer","sei","beitrag","user","seit","zeichen","tba","datenschutzerklärung","premium","nutzungsbedingungen","nutzungsrechte","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","fullscreen","statista","club","sagte","borenda","spreepicture","shopübersicht","herr","imago","dobovisek","barenberg","heinlein","armbrüster","kaess","münchenberg","büüsker","tsereteli","konietzny","klenkes","hauptstadtstudio","newsletter","premiumbereich","nachrichtenpodcast","karrierespiegel","ganslmeier","heißler","zerback","böddeker","frage","glaube","vorstellen","denken","beispiel","sozusagen","na","picture alliance")

stopwords <- c(german_stopwords_full, mystopwords)
stopwords <- unique(stopwords)

# 3
btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords)
```

## month & document number
```{r}
btw %>%
  mutate(month = month(date),
         week = week(date),
         articleID = as.numeric(rownames(btw)),
         site = ifelse(site=="bild.de","Bild.de",site),
         site = ifelse(site=="focus.de","FOCUS ONLINE",site),
         site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
         site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
         site = ifelse(site=="deutschlandfunk.de","Deutschlandfunk.de",site),
         site = ifelse(site=="tagesschau.de","Tagesschau.de",site)) -> btw
```

### check words with high tf-idf 
```{r}
token <- btw %>%
  group_by(site) %>%
  unnest_tokens(word, text_cleaned) %>%
  dplyr::count(site, word, sort = TRUE)  %>%
  bind_tf_idf(word, site, n) %>%
  dplyr::arrange(desc(tf_idf))

@@

```{r}
btw %>% filter(grepl("Heckmann",text)) %>% select(text,text_cleaned) %>% sample_n(1) %>% htmlTable(align="l")
```

### 2018-01-09 paper/R/03_stm.Rmd
step

rm(list=ls())
# Functions
source("func/topic-modelling-functions.R")
```

@@

## Preparation
### Build Corpus
```{r eval=FALSE, include=FALSE}
# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

@@

```{r}
k = 28 # Topics

t1 <- Sys.time()
stmOut <- stm(documents = out$documents,
           vocab = out$vocab,
           K=k,
           prevalence = ~site+s(month),
           data=out$meta,
           max.em.its = 75,
           seed =8458159,
           init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

>>>>

#rm(list=ls())
# Functions
```

@@

## Preparation
### Build Corpus
```{r eval=FALSE, include=FALSE}
# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","week")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)

save(btw, out, file="../output/btw_combined.Rda")
```

@@

```{r}
k = 50 # Topics

t1 <- Sys.time()
stmOut <- stm(documents = out$documents,
           vocab = out$vocab,
           K=k,
           prevalence = ~site+s(week),
           data=out$meta,
           #max.em.its = 150,
           seed =8458159,
           init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

### 2018-01-09 paper/R/04_regression.Rmd
step

#rm(list=ls())
col <- brewer.pal(6,"Dark2")
```

# Load Data
```{r caching, echo = FALSE}
load("../output/models/STM 15 .Rda")
```

load data "Unique User"
```{r}
## Daily (06-2017 - 12-2017)
unique_user1 <- read_excel("../data/uniqueUser_1.xls")
unique_user2 <- read_excel("../data/uniqueUser_2.xls")

uu_df <- rbind(unique_user1,unique_user2) %>%
  rename(uniqueUser = `Unique User Tag Mio.`,
         site = Dachmarke,
         date = Tag) %>%
  select(date, site, uniqueUser)

rm(unique_user1, unique_user2)
```

# Description of Data

### Unique User 
```{r}
p <- uu_df %>%
  filter(date > as.Date("2017-05-31")) %>%
  ggplot(aes(date, uniqueUser, color=site)) +
  geom_line() +
  geom_vline(aes(xintercept=as.POSIXct("2017-09-24")),
             linetype = 2, color="grey50") +
  scale_color_manual(values = col[c(1,2,3,4,6,7)]) +
  theme(
      #legend.position   = "none",
      legend.text       =  element_text(size=6),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    ) +
  labs(x="", y="", color="", title = "", 
      caption = "
  Source: AGOF (www.agof.de)
      " )

#ggplotly(p)
ggsave(plot= p,
filename = "../figs/uniqueUser.png", device = "png",
width = 6, height = 4,
        dpi = 600
)
```

@@

@@

@@

## Topic Proportion
```{r fig.height=7, fig.width=9}
library(stm)
png("../figs/topic_proportion.png")
plot(stmOut, type = "summary", xlim = c(0,.3), n = 5, 
     custom.labels = topicLabel$topic_name, 
     family = "Roboto", main = "", text.cex = 1)
dev.off()
```

@@

```{r}
btw %>% filter(topic==8) %>%
  filter(gamma>=0.5) %>%
  select(url, gamma) %>% htmlTable::htmlTable(align="l")
```

```{r}
label[1]
```

@@

```{r}
prep <- estimateEffect(1:15 ~site + s(month),
                       stmOut, meta=out$meta, uncertainty = "Global")
```

@@

```{r}
for (i in 1:25){
  plot(prep, "month", method = "continuous", topics = i,
       printlegend = F,
       ylab = "", xlab = "Mean topic proportion in corpus",
       main = paste0("Topic ",i,": ",topicLabel$topic_name[i]))
}

@@

## Topic Timeline
```{r Data for topic trends chart, message=FALSE, warning=FALSE}
set.seed(7292)
btw.reg %>% 
  mutate(date = as.POSIXct(date),
         allocation = 1) %>%
  mutate(post_period = 
           date %>% with_tz("Europe/Paris") %>% 
           floor_date("week")) %>%
  # Summarise into tidy dataframe
  group_by(post_period, topic, topic_name) %>% dplyr::summarise(articles = sum(allocation)) %>%
  # Mark peaks 
  group_by(topic_name) %>% dplyr::mutate(peak = ifelse(articles==max(articles),1,0)) -> chart_topic_trends.dt
```

```{r message=FALSE, warning=FALSE}
ggsave(
  plot = {
    ggplot(chart_topic_trends.dt, 
       aes(post_period, articles, color=topic_name)) +
  geom_line() +
  scale_color_manual(
            values = rainbow(28) %>% 
              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
          ) +
  geom_text_repel(data=subset(chart_topic_trends.dt,peak==1),
            aes(post_period,articles,label=paste(topic,topic_name,sep=":")),
            size=2.8) +
      geom_vline(aes(xintercept=as.POSIXct("2017-09-23")),
                 linetype = 2, color="grey20") +
      geom_vline(aes(xintercept=as.POSIXct("2017-11-19")),
                 linetype = 2, color="grey20") +
  ylim(c(0,200)) +
    theme(
      legend.position   = "none",
      #plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.grid        = element_blank(),
      #panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )
  },
  device = "png",
  filename = "../figs/topic-timeline.png",
  dpi = 600, height = 5, width = 8
)
```

>>>>

rm(list=ls())
col <- brewer.pal(6,"Dark2")
```

# Load Data
```{r caching, echo = FALSE}
load("../output/models/STM 20 .Rda")
```

@@

# topicLabel <- as.data.frame(label$topics)
# 
# topicLabel <- topicLabel %>% 
#   transmute(topic = rownames(.),
#              topic_name = paste(V1,V2,V3,V4,V5, sep=","))

@@

```{r}
labelTopics(stmOut, 19, n=10)
```

@@

## Topic Proportion
```{r fig.height=7, fig.width=9}
library(stm)
png("../figs/topic_proportion.png")
plot(stmOut, type = "summary", xlim = c(0,.5), n = 5, 
     custom.labels = topicLabel$topic_name, 
     family = "Roboto", main = "", text.cex = 1)
dev.off()
```

@@

@@

```{r}
prep <- estimateEffect(1:15 ~site + s(week),
                       stmOut, meta=out$meta, uncertainty = "Global")
```

@@

```{r}
for (i in 1:25){
  plot(prep, "week", method = "continuous", topics = i,
       printlegend = F,
       ylab = "", xlab = "Mean topic proportion in corpus",
       main = paste0("Topic ",i,": ",topicLabel$topic_name[i]))
}

@@

## Topic Timeline
```{r Data for topic trends chart, message=FALSE, warning=FALSE}
set.seed(7292)
btw %>% 
  mutate(date = as.POSIXct(date),
         allocation = 1) %>%
  mutate(post_period = 
           date %>% with_tz("Europe/Paris") %>% 
           floor_date("week")) %>%
  # Summarise into tidy dataframe
  group_by(post_period, topic, topic_name) %>% dplyr::summarise(articles = sum(allocation)) %>%
  # Mark peaks 
  group_by(topic_name) %>% dplyr::mutate(peak = ifelse(articles==max(articles),1,0)) -> chart_topic_trends.dt
```

```{r message=FALSE, warning=FALSE}
ggsave(
  plot = {
    ggplot(chart_topic_trends.dt, 
       aes(post_period, articles, color=topic_name)) +
  geom_line() +
  scale_color_manual(
            values = rainbow(15) %>% 
              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
          ) +
  geom_text_repel(data=subset(chart_topic_trends.dt,peak==1),
            aes(post_period,articles,label=paste(topic,topic_name,sep=":")),
            size=2.8) +
      geom_vline(aes(xintercept=as.POSIXct("2017-09-23")),
                 linetype = 2, color="grey20") +
      geom_vline(aes(xintercept=as.POSIXct("2017-11-19")),
                 linetype = 2, color="grey20") +
  ylim(c(0,200)) +
    theme(
      legend.position   = "none",
      #plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.grid        = element_blank(),
      #panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )
  },
  device = "png",
  filename = "../figs/topic-timeline.png",
  dpi = 600, height = 5, width = 8
)
```

### 2018-01-09 paper/R/pageImpr.Rmd
step

>>>>

```{r}
p <- uu_df %>%
  filter(date > as.Date("2017-05-31")) %>%
  ggplot(aes(date, uniqueUser, color=site)) +
  geom_line() +
  geom_vline(aes(xintercept=as.POSIXct("2017-09-24")),
             linetype = 2, color="grey50") +
  scale_color_manual(values = col[c(1,2,3,4,6,7)]) +
  theme(
      #legend.position   = "none",
      legend.text       =  element_text(size=6),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    ) +
  labs(x="", y="", color="", title = "", 
      caption = "
  Source: AGOF (www.agof.de)
      " )

#ggplotly(p)
ggsave(plot= p,
filename = "../figs/uniqueUser.png", device = "png",
width = 6, height = 4,
        dpi = 600
)
```
